Lifting CDCL to Relational Domains

### 2016-10-13 experiments.tex
minor

\paragraph {\em Decision Heuristics} We compare the performance of 
different decision heuristic on our benchmarks.  We observe that 
the ordered heuristic outperforms other heuristics on control-intensive 
benchmarks due to its ability to prioritize decisions on variables that 
appears in conditional branches.  For straight-line code and most of 
the bit-vector regression suite, random heuristics performs the best.  
Whereas, the activity based heuristics such as Berkmin heuristic which 
works well in propositional cases performs best for safe benchmarks 
that encountered maximum number of conflicts to prove safety.

\paragraph {\em Clause Learning}

>>>>

\paragraph {\em \textbf{Decision Heuristics}} We compare the performance of 
different decision heuristic on our benchmarks.  We observe that 
the ordered heuristic outperforms other heuristics on control-intensive 
benchmarks due to its ability to prioritize decisions on variables that 
appears in conditional branches.  For straight-line code and most of 
the bit-vector regression suite, random heuristics performs the best.  
Whereas, the activity based heuristics such as Berkmin heuristic which 
works well in propositional cases performs best for benchmarks that 
encountered the maximum number of conflicts to prove safety, thus allowing 
the heuristics to choose the decison variable from the set of learnt clauses.

\paragraph {\em \textbf{Clause Learning}}

### 2016-10-13 learning.tex
minor

The first-UIP algorithm in SAT solver works on a data structure called 
{\em implication graph} that computes a cut that suffices to produce a 
conflict.  The trail in ACDCL implicitly encodes a graph structure called 
{\em abstract conflict graph}, which records the dependencies between 
deductions made during abstract model search phase.  For example, consider a
formula $\varphi:= (x=5 \wedge y=x \wedge y=y+x \wedge y \leq 0)$ with current 
abstract valuation $v:= (x=[5,5])$.  
Figure~\ref{conflict} shows a snapshot of abstract implication graph that 
stores the deductions obtained from abstract model search using octagon domain.  
An arrow in the graph indicate that the predecessors of each node $n$ are 
sufficient to deduce $n$.  The last deduction conflict with the constraint 
$(y \leq 0)$.  Every cut in the graph, marked as {\em cut0, cut1}, provides a 
reason for conflict that can be used in learning.  An UIP is a special node such 
that any path from the last decision node to the conflict node must pass 
through it.  Unlike a SAT solver, a UIP in ACDCL may involve meet irreducibles 
that involves the same variables.  The first-UIP is a node closest to the 
conflict, and the last UIP is the decision node itself.  Computing UIPs ensures 
asserting cuts, that is, it yields clauses that generates new deduction after 
backtracking.  For our example, there exists multiple incomaparable reasons 
for conflict.  Here, cut0 is the first UIP.  Choosing cut0 yields a learnt 
clause $L_0: (x+y<15 \vee -x-y<-15 \vee -x+y<5 \vee x-y<-5 \vee y-10<0 \vee 
-y+10<0)$.  A learnt clause $\mathcal{L}$ is obtained by negating the reason 
for conflict.  
%
\begin{figure}
%\caption{An example of Octagon}\label{octagon}
\scalebox{.65}{\import{figures/}{conflict_graph.pspdftex}}
\label{conflict}
\end{figure} 
%    
\paragraph {\em Backjumping:}
A backjumping procedure undo all the assignments in the trail up to 
a decision level that restores the solver to a consistent state 
(non-conflicting).  The backjumping level is defined by the literal 
of the conflict clause that is closest to the root (decision level 0) 
where the conflict clause is still unit. If a conflict clause is 
globally unit, then the backjumping level is the root of the search tree.

>>>>

The first-UIP algorithm in SAT solver works on a data structure called 
{\em implication graph} that computes a cut that suffices to produce a 
conflict.  The trail in ACDCL implicitly encodes a graph structure called 
{\em abstract conflict graph}, which records the dependencies between 
deductions made during abstract model search phase.  For example, consider a
formula $\varphi:= (x=5 \wedge y=x \wedge y=y+x \wedge y \leq 0)$ with current 
abstract valuation $v:= (x=5)$.  
Figure~\ref{conflict} shows a snapshot of an abstract conflict graph that 
stores the deductions obtained from abstract model search using octagon domain.  
An arrow in the graph indicate that the predecessors of each node $n$ are 
sufficient to deduce $n$.  The last deduction conflict with the constraint 
$(y \leq 0)$.  Every cut in the graph, marked as {\em cut0, cut1}, provides a 
reason for conflict that can be used in learning.  An UIP is a special node such 
that any path from the last decision node to the conflict node must pass 
through it.  Unlike a SAT solver, a UIP in ACDCL may involve meet irreducibles 
that involves the same variables.  The first-UIP is a node closest to the 
conflict, and the last UIP is the decision node itself.  Computing UIPs ensures 
asserting cuts, that is, it yields clauses that generates new deduction after 
backtracking.  For our example, there exists multiple incomaparable reasons 
for conflict.  Here, cut0 is the first UIP.  Choosing cut0 yields a learnt 
clause $L_0: (x+y<15 \vee -x-y<-15 \vee -x+y<5 \vee x-y<-5 \vee y-10<0 \vee 
-y+10<0)$.  A learnt clause $\mathcal{L}$ is obtained by negating the reason 
for conflict.  
%
\begin{figure}
%\caption{An example of Octagon}\label{octagon}
\scalebox{.65}{\import{figures/}{conflict_graph.pspdftex}}
\label{conflict}
\end{figure} 
%    
\paragraph {\em Backjumping:}
A backjumping procedure undo all the assignments in the trail up to 
a decision level that restores the solver to a consistent state 
(non-conflicting).  The backjumping level is defined by the literal 
of the conflict clause that is closest to the root (decision level 0) 
where the conflict clause is still unit. If a conflict clause is 
globally unit, then the backjumping level is the root of the search tree.
